---
title: "Analysis"
format: html
editor: visual
---

# Libraries

```{r}
library(tidyverse)
library(broom)
library(ggthemes)
library(ggrepel)
library(tidygraph)
library(ggraph)
library(googlesheets4)
library(gtsummary)
library(gt)
library(gtExtras)

```

# Data

```{r}
ss <- "https://docs.google.com/spreadsheets/d/1xzpre5Ej_7OEGRU4EA7KZuMQnSz5YCyTx5Sdbml6bQE/edit#gid=0"

df_main_raw <- read_sheet(ss, sheet = "Main")
geo_locations_raw <- read_sheet(ss, sheet = "locations_coord", range = "B:F")

df_companies <- read_sheet(ss, sheet = "CompanyAnalysis")

cities <- read_csv2("data/ai_cities_cleaned.csv") # Needs to be checked
regions_raw <- read_csv2("data/locations_regions.csv")
regions_pop_raw <- read_csv2("data/regions_population.csv")

workforce_gdp <- tribble(
  ~Country, ~Workforce, ~GDP_per_capita_kUSD, ~GDP_total_billion_USD, 
  "SE", 5.2, 56, 592,  
  "NO", 2.8, 109, 593,
  "DK", 3.0, 67, 400
  )

```

# Wrangel

```{r}

regions <- regions_raw %>% 
  separate(location, into = c("location", "country"), sep = "-") %>% select(-country) # not all country are correct

region_pop <- regions_pop_raw %>% 
  separate(region, into = c("region", "country"), sep = "\\(") %>%
  mutate(country = str_remove_all(country, "\\)"), 
         region = str_squish(region))


location_region_pop <- cities %>% 
  separate(location, into = c("location", "country"), sep = "-") %>%
  select(-country) %>%
  left_join(regions) %>%
  rename(loc_pop = population) %>%
  mutate(region = ifelse(region == "Telemark", 
                         str_replace(region, "Telemark", "Vestfold og Telemark"),
                         region)) %>%
  left_join(region_pop, by = "region") %>%
  rename(reg_pop = population)


geo <- geo_locations_raw

jobs <- df_main_raw %>% 
  inner_join(geo, by = "Location") %>%
  mutate(Country = case_when(
    str_detect(ID, pattern ="^1") ~ "SE", 
    str_detect(ID, pattern ="^2") ~ "NO",
    str_detect(ID, pattern ="^3") ~ "DK"
  )) %>%
  mutate(Scrape_date = lubridate::ymd(Scrape_date)) %>%
  filter(Scrape_date >= "2023-08-20")

max(jobs$Scrape_date)

companies <- df_companies %>% slice(-1)

```



# Descriptives

## New jobs over time

-   plot describing number of new jobs per month

```{r}
jobs_over_time <- jobs %>% 
  mutate(year = lubridate::year(Scrape_date), month = lubridate::month(Scrape_date)) %>% 
  group_by(year, month, Country) %>%
  summarise(n =n()) %>%
  unite("ym", year:month, sep = "-") %>%
  ungroup() %>%
  mutate(ym = as_factor(ym))

jobs_over_time %>% 
  ggplot(aes(ym, n, fill= Country)) + 
  geom_col() + 
  scale_fill_viridis_d()+
  theme_minimal() +
  labs(x= "", y= "Nr. of new jobs")
  
ggsave("figs/jobs_over_time.png", dpi = 600)

```


## New jobs and country stats

-   simple comparision of main stats between countries

```{r}

comp <- jobs %>% 
  select(Country, Company) %>% 
  unique() %>% 
  group_by(Country) %>% 
  count(name="nr_comp")

tbl_country_comp <- jobs %>% 
  group_by(Country) %>% 
  summarise(Jobs = n(), .groups = "drop") %>%
  mutate(perc = Jobs/sum(Jobs)*100) %>%
  left_join(comp) %>%
  mutate(perc_c = nr_comp/sum(nr_comp)*100) %>%
  left_join(workforce_gdp) 

gt_tbl_country_comp <- tbl_country_comp %>% 
  gt(rowname_col = "Country") %>%
  tab_stubhead(label = "Country") %>%
  grand_summary_rows(
    columns = -Country,
    fns = list(
      Total ~sum(.)
    )
  ) %>% 
  fmt_number(decimals = 0) %>%
  tab_spanner(
    columns = c(Jobs, perc),
    label = "New Jobs"
  ) %>%
  tab_spanner(columns = c(nr_comp, perc_c),
              label = "Organisations") %>%
  tab_spanner(columns = c(Workforce, GDP_total_billion_USD, GDP_per_capita_kUSD),
              label = "Country Statistics") %>%
  cols_label(
    Jobs ~ "Nr.",
    perc ~ "(%)",
    nr_comp ~ "Nr.",
    perc_c ~ "(%)",
    Workforce ~ "Labour<br>(mil.)",
    GDP_total_billion_USD ~ "GDP<br>(b$)",
    GDP_per_capita_kUSD ~ "GDP/Cap.<br>(k$)",
    .fn = md
  ) %>% gt_theme_espn()

gtsave(gt_tbl_country_comp, filename = "tables/countries_jobs.png")

```

## Overview company descriptives

-   Here are two tables. First one long with all companies. Then three smaller ones, one for each country.

```{r}

companies_overview <- jobs %>%
  group_by(Country, Company) %>%
  summarise(n=n()) %>%
  arrange(desc(n)) %>%
  mutate(share = n/sum(n)*100) %>%
  ungroup()

long_table <- companies_overview %>%
  gt(rowname_col = "Company",
     groupname_col = "Country") %>%
  summary_rows(
    columns = c(n, share),
    fns = list(
    Total ~ sum(.)
    ),
    fmt = ~ fmt_number(., decimals = 0),
  ) %>%
  summary_rows(
    columns = n,
    fns = list(
      Min ~ min(.), 
      Max ~ max(.),
      Average ~ mean(.),
      Nr_org. ~ length(.)
      ),
    fmt = ~ fmt_number(., decimals = 0)
  ) %>%
  fmt_number(columns = share, decimals = 1) %>%
  grand_summary_rows(
    columns = n,
    fns = list(
      Total ~ sum(.),
      Min ~ min(.),
      Max ~ max(.),
      Average ~ mean(.),
      Nr_org. ~ length(.)
      ),
    fmt = ~ fmt_number(., decimals = 0)
    ) %>%
  cols_label(
    n ~ "New Jobs",
    share ~ "Share (%)"
  )

long_table

gtsave(long_table, filename = "tables/long_tbl_companies.pdf")


```

Per country tables

```{r}

tot_jobs <- sum(companies_overview$n)
top_10 <- companies_overview %>%
  # Group by country to perform operations within each country
  group_by(Country) %>%
  # Arrange by descending n within each group
  arrange(desc(n), .by_group = TRUE) %>%
  # Create a new column to identify top 10 companies considering ties
  mutate(Rank = rank(-n, ties.method = "first")) %>%
  # Adjust Company name, keeping top 10 and any ties at the 10th place, lump the rest as 'Other'
  mutate(Company = ifelse(Rank <= 10, Company, "Other")) %>%
  # Regroup to combine 'Other' entries
  group_by(Country, Company) %>%
  # Summarize to aggregate counts for each company or 'Other'
  summarize(n = sum(n)) %>%
  mutate(share = n/sum(n)*100, share_tot = n/tot_jobs*100) %>%
  # Arrange within each country to ensure 'Other' appears last and companies are sorted by n
  arrange(Country, desc(n)) %>%
  mutate(Company = fct_infreq(Company) %>% fct_relevel("Other", after = Inf)) %>%
  # Final arrange to ensure 'Other' is last
  arrange(Country, Company == "Other") %>%
  ungroup() %>%
  mutate(Company = as.character(Company)) %>%
  mutate(Company = str_trunc(Company, width =20, ellipsis = "."))


top10 <- function(cc){
  
  ll <- case_when(
    cc== "DK" ~ "Denmark",
    cc== "SE" ~ "Sweden",
    cc == "NO" ~"Norway"
  )
  
  top_10 %>% 
  filter(Country == cc) %>%
  select(-Country) %>%
  gt(rowname_col = "Company") %>%
  tab_stubhead(label = "Companies") %>%
  grand_summary_rows(
    columns = c(n, share, share_tot),
    fns = list(
      Total = ~ sum(.)
    ), 
    fmt = ~fmt_number(., columns = share_tot, decimals = 1)) %>%
  fmt_number(columns = c(share, share_tot), decimals = 1) %>%
  tab_spanner(
    columns = everything(),
    label = ll
  ) %>% 
  cols_label(
    n~"New jobs",
    share ~ "(%)",
    share_tot ~ "Total(%)"
  ) %>%
  gt_theme_espn()
}


dk <- top10("DK")
no <- top10("NO")
se <- top10("SE")

gtsave(dk, filename = "tables/dk_comp.png")
gtsave(no, filename = "tables/no_comp.png")
gtsave(se, filename = "tables/se_comp.png")
```





## Overview: Jobs per sector

```{r}
tbl <- jobs %>%
  inner_join(df_companies %>% 
               select(Name, Industry_Sector), by = c("Company"="Name")) %>%
  rename(Sector = Industry_Sector)

gt_tbl <- tbl %>%
  tbl_cross(Sector, Country, percent = "cell") %>%
  as_gt() %>%
  gt_theme_espn()

gt_tbl

```




## Overview: job_roles

```{r}
jobs %>% 
  rename("Job type" = Job_role) %>%
  gtsummary::tbl_cross(row = "Job type", col = Country, percent = "cell", missing = "ifany") %>%
  as_gt() %>%
  gt_theme_espn()

```


# Places - Where

## A new map?

```{r}




```

## Correlation between jobs and populations in specific locations and in regions

-   In this section we first check the correlation between new jobs for the different locations
-   We then check the correlation between new jobs and regions.

### Wrangling the data

```{r}
location_new_jobs <- jobs %>% 
  group_by(Location) %>%
  summarise(new_jobs = n()) %>% rename(location = Location)

location_all <- location_region_pop %>% 
  left_join(location_new_jobs) %>%
  filter(!is.na(new_jobs)) # there is some na's since the file pop_ai reads locations from sheet "geo_locations_raw" without checking if there are jobs in the harmonized time period. 


```

### lm new jobs ~ locations - all countries
### lm new jobs \~ locations - all countries

```{r}
lm_location <- lm(new_jobs ~ loc_pop, data = location_all)
summary(lm_location)
tidy(lm_location)

glance(lm_location)

```

### lm new jobs \~ locations - per country

### lm new jobs ~ locations - per country
```{r}
lm_data <- location_all %>% 
  group_by(country) %>%
  nest(data = -country) %>% 
  mutate(lm = map(data, ~lm(new_jobs ~ loc_pop, data = .))) %>%
  mutate(tidy = map(lm, ~tidy(.)),
         glance = map(lm, ~glance(.)), 
         aug = map(lm, ~augment(.))) 

lm_data %>% select(country, glance) %>% unnest(glance)

outliers <- lm_data %>%
  mutate(outliers = map(aug, ~.x %>%
                          mutate(outlier = abs(.resid) > 2*sd(.resid)))) %>%
  select(country, data, outliers) %>%
  mutate(location = map(data, ~.x$location),
         region = map(data, ~.x$region)) %>%
  select(-data) %>%
  unnest(c(location, region, outliers)) %>%
  relocate(location:region, .after = "country") %>%
  filter(outlier)

```

### Plot between location and new jobs

-   add p-value and R.squared to plot

```{r}
location_all %>% 
  ggplot(aes(x= round(loc_pop/1e3), y= new_jobs, colour = country)) + 
  geom_smooth(aes(round(loc_pop/1e3), new_jobs),
              color = "darkred", linetype = "dashed",
              linewidth = 2.5, alpha = 0.7,
              method = "lm", se=F, 
              inherit.aes = F, show.legend = F)+
  geom_smooth(method = "lm", show.legend = F, se = F, 
              linewidth = 1.5, alpha =0.7)+
  geom_point(aes(size= new_jobs), alpha = 0.7) + 
  geom_label_repel(aes(label = paste0(location, "\n(",region,")"),
                       color = country), 
                  size = 2, alpha =1,
                  show.legend = F,
                  data = outliers)+
  scale_color_colorblind("Country")+
  scale_size_continuous(range = c(1,4)) +
  labs(x= "Population in thousands", y= "Nr. of new jobs") +
  theme_minimal() +
  guides(size = "none")+
  theme(legend.position = "top")
ggsave("figs/location_new_jobs.png", dpi = 600, width = 8, height = 4)
```

-   For all three countries it appears to be a linear relationship
-   It appears to be more outliers in Norway and Denmark than in Sweden. However, some locations are close to another and part of a larger region


### lm new jobs \~ region

### lm new jobs ~ region
-   now same thing but for all regions

```{r}
region_new_jobs <- location_all %>% 
  group_by(region, reg_pop, country) %>%
  summarise(new_jobs = sum(new_jobs))

lm_regions <- lm(new_jobs ~ reg_pop, data = region_new_jobs)
glance(lm_regions)

```
#### lm new jobs ~ region per country

#### lm new jobs \~ region per country

-   and regions per country

```{r}

lm_data_reg <- region_new_jobs %>% 
  group_by(country) %>%
  nest(data = -country) %>% 
  mutate(lm = map(data, ~lm(new_jobs ~ reg_pop, data = .))) %>%
  mutate(tidy = map(lm, ~tidy(.)),
         glance = map(lm, ~glance(.)), 
         aug = map(lm, ~augment(.))) 

lm_data_reg %>% select(country, glance) %>% unnest(glance)

outliers_reg <- lm_data_reg %>%
  mutate(outliers = map(aug, ~.x %>%
                          mutate(outlier = abs(.resid) > 2*sd(.resid)))) %>%
  select(country, data, outliers) %>%
  mutate(region = map(data, ~.x$region)) %>%
  select(-data) %>%
  unnest(c(region, outliers)) %>%
  relocate(region, .after = "country") %>%
  filter(outlier)

```


### Plot between region and new jobs

-   higlight outlier
-   add p and r.squared

```{r}
region_new_jobs <- location_all %>% 
  group_by(region, reg_pop, country) %>%
  summarise(new_jobs = sum(new_jobs))


region_new_jobs %>% 
  ggplot(aes(round(reg_pop/1e3), new_jobs, 
             colour = country)) + 
  geom_smooth(linewidth = 1.5, alpha = 0.7, 
              method = "lm", se=F, inherit.aes = T, show.legend = F)+
  geom_smooth(aes(round(reg_pop/1e3), new_jobs),
              color = "darkred", linetype = "dashed",
              linewidth = 1.5, alpha = 0.7,
              method = "lm", se=F, 
              inherit.aes = F, show.legend = F)+
  geom_point(aes(size= new_jobs), alpha = 0.7) + 
  geom_label_repel(aes(label = region,
                       color = country), 
                  size = 2, alpha =1,
                  show.legend = F,
                  data = outliers_reg)+
  geom_label_repel(aes(label = region,
                       color = country), 
                  size = 2, alpha =1,
                  show.legend = F)+
  scale_color_colorblind(" ")+
  scale_size_continuous(range = c(1,4)) +
  guides(size = "none")+
  labs(x= "Population in thousands", y= "Nr. of new jobs") +
  theme_minimal() +
  theme(legend.position = "top")
ggsave("figs/all_region_pop.png", dpi= 600, width = 8, height = 4)



```

-   From a Nordic perspectives significantly more jobs are created in Oslo, Rogland, Vestland
-   Too few regions to split between countries.


# Companies - who

## Distribution

```{r}
df_distribution <- jobs %>% 
  count(Company, Country) %>% 
  filter(!Company == "!!!NEW_COMPANY!!!")

df_distribution %>% 
  ggplot(aes(n, Country, fill = Country), alpha = 0.5) + 
  geom_violin() + 
  scale_fill_colorblind() + 
  theme_grey() +
  theme(legend.position = "bottom") +
  labs(x = "", y = "")

ggsave(filename = "figs/violine.png", width = 6, height = 4, dpi = 600)


```


## Share of companies

```{r}

prop <- df_distribution %>% filter(Country =="SE") %>% 
  ungroup() %>% 
  slice_max(prop = 0.8, order_by = n)

prop <- df_distribution %>% filter(Country =="SE") %>% 
  ungroup() %>% 
  mutate(ff = fct_lump_n(Company, n = 10, w=n))

df_distribution %>% forcats::fct_lump_prop()

df_distribution %>% 
  group_by(Country, n) %>%
  summarise(nr_companies = n())

```


## Bipartitie - Companies Countries

```{r}

df_gs <- jobs %>% 
  count(Company, Country, name = "weight") %>% 
  filter(!Company == "!!!NEW_COMPANY!!!")


nr_jobs_comp <- jobs %>% count(Company, name = "jobs") %>% 
  filter(!Company == "!!!NEW_COMPANY!!!") %>% rename(name = Company)
nr_jobs_country <- jobs %>% 
  count(Country, name = "jobs") %>% 
  rename(name = Country)
node_data <- bind_rows(nr_jobs_comp, nr_jobs_country)

gs <- df_gs %>% as_tbl_graph(directed = FALSE) %N>%
  mutate(type = ifelse(name %in% df_gs$Company, "actor", "country")) %>%
  mutate(ctrl = centrality_degree()) %>%
  left_join(node_data)
  

nodes <- gs %N>% as_tibble()
edges <- gs %E>% as_tibble()



```

## Plot

```{r}
# Plotting with ggraph

set.seed(14)
ggraph(gs, layout = "stress") +
  geom_edge_link(aes(edge_width = weight), edge_alpha =0.3, edge_color = "lightgrey", show.legend = FALSE) + # Adjust alpha or width based on MSEK_EM if needed
  geom_node_point(aes(color = type, shape = type, size = jobs), show.legend = FALSE) +
  geom_node_text(aes(label = ifelse(jobs >5 | ctrl >1, name, ""),
                     size = ctrl), 
                 repel = TRUE, hjust = 0.5, vjust = 0, show.legend = FALSE) +
  theme_graph() +
  scale_color_manual(values = c("actor" = "lightblue", "country" = "orange")) +
  scale_size(range = c(2,10))+
  scale_edge_width(range = c(2, 4))+
  ggtitle("")
ggsave("figs/two_mode_countries.png", dpi = 600)
```

# Most new jobs are created by companies that only recruit in one country.

```{r}
most_jobs <- nodes %>% 
  filter(type == "actor") %>%
  mutate(type = ifelse(ctrl == 1, "single", "multiple"))

most_jobs %>% group_by(type)  %>%
  summarise(jobs = sum(jobs))

most_jobs %>% filter(type == "multiple") %>% 
  left_join(companies %>% select(Name, Industry_Sector), by = c("name" = "Name")) %>%
  group_by(Industry_Sector) %>%
  summarise(Jobs = sum(jobs)) %>%
  arrange(desc(Jobs)) %>%
  bind_rows(summarise(., Industry_Sector = "Total", Jobs = sum(Jobs))) %>%
  gt()


```



# H2 The creation of new jobs within the hydrogen economy is positively correlated with sector and job roles

```{r}
companies_sector <- companies %>% select(Company = Name, Sector = Industry_Sector)

tmp <- jobs %>%
  left_join(companies_sector) %>%
  group_by(Country, Sector, Job_role) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(Country, Sector, Job_role, fill = list(n= 0)) %>%
  filter(!is.na(Job_role) & !is.na(Sector))

tmp_no <- tmp %>% filter(Country == "NO")
tmp_dk <- tmp %>% filter(Country == "DK")
tmp_se <- tmp %>% filter(Country == "SE")

lm_all <- lm(n ~ Sector+Job_role, data = tmp)
t1 <- gtsummary::tbl_regression(lm_all) %>% add_significance_stars()

lm_no <- lm(n ~ Sector+Job_role, data = tmp_no)
t2 <- gtsummary::tbl_regression(lm_no) %>% add_significance_stars()

lm_dk <- lm(n ~ Sector+Job_role, data = tmp_dk)
t3 <- gtsummary::tbl_regression(lm_dk) %>% add_significance_stars()

lm_se <- lm(n ~ Sector+Job_role, data = tmp_se)
t4 <- gtsummary::tbl_regression(lm_se) %>% add_significance_stars()

t_merge <- tbl_merge(
  tbls = list(t1, t2, t3, t4),
  tab_spanner = c("**All Countries**", "**Norway**", "**Denmark**", "**Sweden**")
)

t_merge %>% as_gt() %>% gtsave(filename = "tables/sector_jobroles_lm.png")
```


# Share of total jobs

```{r}
se <- tbl %>% count(Country) %>% subset(Country == "SE", n) %>% pull()
dk <- tbl %>% count(Country) %>% subset(Country == "DK", n) %>% pull()
no <- tbl %>% count(Country) %>% subset(Country == "NO", n) %>% pull()

sector <- tbl %>%
  count(Industry_Sector, Country) %>%
  complete(Industry_Sector, Country, 
           fill = list(n = 0)) %>%
  relocate(Country) %>%
  mutate(share = )
  pivot_wider(names_from = Country, values_from = n)

```




```{r}
sector <- tbl %>%
  count(Industry_Sector, Country) %>%
  complete(Industry_Sector, Country, 
           fill = list(n = 0)) %>%
  relocate(Country)

test_chi_data <- sector %>% pivot_wider(names_from = Industry_Sector, values_from = n)
chi_sq_res <- chisq.test(select(test_chi_data, -Country))

cor.test()

fisher.test(select(test_chi_data, -Country))

write_csv(sector, "tables/sectors.csv")
  

sector %>% 
  ggplot(aes(n, Industry_Sector, fill= Country)) + 
  geom_col(position = "fill")+
  theme_fivethirtyeight()+
  scale_fill_fivethirtyeight()+
  labs(x = "", y = "Proportion")
ggsave("figs/sector_focus.png")
```



```{r}

sector %>% ggplot(aes(n, Industry_Sector, fill = Country)) + 
  geom_col() + 
  facet_wrap(~Country, scales = "fixed") +
  theme_fivethirtyeight()+
  scale_fill_fivethirtyeight()

ggsave("figs/sector_focus2.png", width = 14, height = 8)


```
