---
title: "End_Use"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Libraries

```{r}
library(tidyverse)
library(googlesheets4)
library(ggthemes)
library(gtExtras)
library(tidygraph)
library(igraph)
library(ggraph)
library(lsr)
library(corrplot)
```

# Data

```{r}

ss <- "https://docs.google.com/spreadsheets/d/1RefL2DMmCoOjCcIiaYgSnuDF34ORQFAZKu3nkaoS6o8/edit?gid=1138676736#gid=1138676736"

# Read project sheet and clean 
df_raw <- read_sheet(ss, sheet = "Projects_2") 

df <- df_raw %>% 
  janitor::clean_names() %>% 
  mutate(date_online = unlist(date_online)) %>%
  mutate(electrolyser_mw = unlist(electrolyser_mw)) %>%
  mutate(date_online = as.numeric(date_online)) %>%
  mutate(electrolyser_mw = as.numeric(electrolyser_mw)) %>%
  mutate(status = str_replace_all(status, "Unknown", "Paused/Cancelled")) %>%
  filter(date_online>=2015)

df_locations <- read_sheet(ss, sheet = "locations")

df_actors <- read_sheet(ss, sheet = "collaborations") 
df_a <- df_actors %>% 
  janitor::clean_names() 

df_c<- df %>%
  select(id, project_name, country, location, date_online, status, technology, electricity, electrolyser_mw, product, end_use_mobility, end_use_heat_power, end_use_grid_export)

comp <- read_sheet(ss,sheet="collaborations")
comp <- comp %>% 
  janitor::clean_names() 

```

# Notes

options: - map - H2 over time - Illustrate actors across - countries, see who connects across multiple projects - illustrate correlation between variables? Here one could also do a cluster analysis - later

## H2 Map?

# H2 over time - Done

Illustrates what year the projects are planned to be operational in different countries - For this figure mention main project - The number of projects per country - And outline main differences.

```{r}
status_colors <- c(
  "Operational" = "#27AE60",      
  "Paused/Cancelled" = "#C0392B", 
  "Feasibility study" = "#D4AC0D", 
  "FID/Construction" = "#2874A6"  
)
```

## Projects online or being planned to be online

```{r}
over_time <- df_c %>% 
  filter(!status %in% c("Paused/Cancelled")) %>%
  group_by(date_online, country, status) %>%
  summarise(n = n(), mw = round(sum(electrolyser_mw, na.rm = TRUE))+2)

over_time %>% 
  ggplot(aes(date_online, mw, fill = status)) + 
  geom_col() + 
  scale_fill_manual(name = "", values = status_colors)+
  scale_x_continuous(breaks = scales::pretty_breaks())+
  scale_y_log10(labels = scales::label_comma())+
  facet_wrap(~country)+
  labs(x= "", y = "") +
  theme_light() +
  theme(legend.position = "bottom", legend.direction = "horizontal")+
  guides(fill = guide_legend(reverse = TRUE))
ggsave("h2_projects/figs_conf/1_over_time_active.png")
```

## Table

```{r}
mw_rates_ish <- df_c %>% 
  group_by( status) %>%
  summarise(n = n(), mw = round(sum(electrolyser_mw, na.rm = TRUE)))

tot <- sum(mw_rates_ish$mw)
mw_rates_ish %>% group_by(status) %>% 
  summarise(mw = sum(mw), 'share [%]' = round(mw/tot, 4)*100, TWH = round(mw*8000/1e6)) %>% arrange(TWH) %>% gt::gt() %>% gt_theme_espn() %>% gt::gtsave("h2_projects/figs_conf/1_table.png")
  

```

## Projects being abandoned

-   quite a few projects being abandon
-   mention the largest one for each country
-   This can however be expected as plan are progressing and tested against reality.

```{r}
over_time_2 <- df_c %>% 
  filter(status %in% c("Paused/Cancelled")) %>%
  group_by(date_online, country, status) %>%
  summarise(n = n(), mw = round(sum(electrolyser_mw, na.rm = TRUE))+2)

over_time_2 %>% 
  ggplot(aes(date_online, mw, fill = fct_rev(as.factor(status)))) + 
  geom_col() + 
  scale_fill_manual(name = "", values = status_colors)+
  scale_x_continuous(breaks = scales::pretty_breaks())+
  scale_y_log10(labels = scales::label_comma())+
  facet_wrap(~country)+
  labs(x= "", y = "", title = "Paused or Cancelled projects") +
  theme_light() +
  theme(legend.position = "none")
ggsave("h2_projects/figs_conf/2_over_time_cancelled.png")
```

# Actors across

-   How connected are projects in countries through single actors?

```{r}
netw_colors <- c(
  "comp" = "#356D94",     
  "country" = "#6C8B72",  
  "project" = "#FFB347"   
)

background <- "#F5F5F5"  

```

```{r}
pr_country <- df_c %>% 
  filter(!status %in% c("Paused/Cancelled", "Unknown")) %>%
  select(id, country, electrolyser_mw)

bi_country <- df_actors %>% 
  inner_join(pr_country) %>%
  group_by(country, comp_name) %>%
  summarise(n = n(), mw = round(sum(electrolyser_mw, na.rm = TRUE)))

comp_mw <- bi_country %>% group_by(comp_name) %>% summarise(mw = sum(mw)) %>% rename(name = comp_name)

gc <- as_tbl_graph(bi_country) %>%
   mutate(type = ifelse(name %in% bi_country$comp_name, "comp", "country")) %>%
  mutate(degree = centrality_degree(mode = "all")) %N>%
  left_join(comp_mw)

nodes_c <- gc %N>% as_tibble()
edges_c <- gc %E>% as_tibble()

set.seed(123)
gc %>% ggraph(layout = "nicely") + 
  geom_edge_link(color = "grey", show.legend = FALSE) + 
  geom_node_point(aes(fill = type, 
                      size = ifelse(type == "comp", log(mw+1), 10), 
                      shape = type), color = "white") + # Node attributes
  geom_node_label(aes(label = 
                        ifelse(
                          (type == "comp" & degree > 1 & mw > 100) |
                          type == "country" & degree > 9, 
                          name, NA), 
                      color = type), repel = TRUE, size = 3) +
  scale_shape_manual(values =  c(21, 22))+
  scale_fill_manual(values = netw_colors)+
  scale_color_manual(values = netw_colors)+
  labs(title = "Actors Cutting Across the Nordic countries", 
       caption = "Most central actors cutting across multiple countries. Each actor is active in projects with a combined capacity of more than 100MW")+
  theme_graph(background = background) + 
  theme(legend.position = 'none')

ggsave("h2_projects/figs_conf/3_actors_across_countries.png", width = 13.33, height = 7.5, units = "in", dpi = 300)

```

## Actors across projects and countries

```{r}

pr_country <- df_c %>% 
  filter(!status %in% c("Paused/Cancelled")) %>% pull(id)

bi_net <- df_actors %>%
  filter(id %in% pr_country) %>% # filter out only active projects
  group_by(project_name, comp_name) %>%
  summarise(n = n())

gs <- as_tbl_graph(bi_net) %N>% 
  mutate(type = ifelse(name %in% bi_net$comp_name, "comp", "project")) %>%
  mutate(degree = centrality_degree(mode = "all"))
  

nodes <- gs %N>% as_tibble()
edges <- gs %E>% as_tibble()

gs %>% ggraph(layout = "nicely") + 
  geom_edge_link(color = "grey", show.legend = FALSE) + 
  geom_node_point(aes(fill = type, size = degree, shape = type), color = "white") + # Node attributes
  geom_node_label(aes(label = 
                        ifelse(
                          type == "comp" & degree > 5 |
                          type == "project" & degree > 9, 
                          name, NA), 
                      color = type), repel = TRUE, size = 3) +
  scale_shape_manual(values =  c(21, 24))+
  scale_fill_manual(values = netw_colors)+
  scale_color_manual(values = netw_colors)+
  labs(title = "Most Central Actors and Projects across the Nordic countries")+
  theme_graph(background = background) + 
  theme(legend.position = 'none') 

ggsave("h2_projects/figs_conf/4_most_central_actors_projects_wide.png")
ggsave("h2_projects/figs_conf/4_most_central_actors_projects_wide.png",  width = 13.33, height = 7.5, units = "in", dpi = 300)

```

## Data on the graph

```{r}
comps <- components(gs)
comps$csize
comps$no
share <- max(comps$csize)/sum(comps$csize)

```

-   The network consist of 25 components,
-   The largest component consist of 302 nodes and 70% of all nodes
