---
title: "MainCleaner0924"
format: html
editor: visual
---

# Libraries

```{r}

```

CHECK WHICH OF THESE LIBRARIES ACTUALLY ARE NEEDED

```{r}
library(data.table)
library(dplyr)
library(tidyr)
library(googlesheets4)
library(zlib)
library(digest)
library(openssl)
library(base64enc)
library(stringr)
```

# Data

## Google

```{r}
ss <- "https://docs.google.com/spreadsheets/d/1xzpre5Ej_7OEGRU4EA7KZuMQnSz5YCyTx5Sdbml6bQE/edit#gid=0"

# Old scrapes
# Swedish scrape
se_Old <- read_sheet(ss, sheet = "se_scrape")

# Norwegian scrape
no_Old <- read_sheet(ss, sheet = "no_scrape")

# Danish scrape
dk_Old <- read_sheet(ss, sheet = "dk_scrape")

# Company name chart
comp_names <- read_sheet(ss, sheet = "company_names")

# Location name chart with extra info
locations <- read_sheet(ss, sheet = "locations_coord")
```

## Latest scrape

For this section to work must the scrapes have been downloaded and put into a local folder which the main directory can access. It is assumed that the Swedish and Norwegian data is in a csv file while the Danish is in a rds file

```{r}
# Swedish scrape
ams_Latest_scrape <- read.csv("ams.csv", sep=";") %>% filter(s_terms.i.=="vätgas*")

# Norwegian scrape
finn_Latest_scrape <- read.csv("finn_no_h2.csv")

#Danish scrape
dk_Latest_scrape <- as.data.frame(readRDS("dk_h2.rds")) #%>% select(!all_text)
```

# Wrangle of scrape

## Prepping a dataframe

```{r}
new_data <- data.frame( ID = numeric(0), Title = numeric(0), Company = numeric(0), 
                        Location = numeric(0), Description = numeric(0), Scrape_date = numeric(0),
                        Hydrogen_relevance = numeric(0), translatedText = numeric(0))
```

## Refining latest scrapes

### Sweden

```{r}
#Compare what is new
new_se <- ams_Latest_scrape[!ams_Latest_scrape$links %in% se_Old$links,] 

# Add ID to our new data
ID <- nrow(se_Old)
IDcol <- c()
for (i in seq_len(nrow(new_se))) {
  ID <- ID + 1
  IDcol <- append(IDcol,10000+ID)
}
new_se <- cbind(IDcol,new_se)

# Choose what to put into clean sheet
new_for_clean_se <- new_se %>% select(IDcol,job_role,company,location,description,scrape_date)
colnames(new_for_clean_se) <- c("ID","Title", "Company","Location","Description","Scrape_date")

# Add to total of new data
new_for_clean_se[c("Hydrogen_relevance", "translatedText")] <- NA
new_data <- rbind(new_data,new_for_clean_se)
```

### Norway

```{r}
#Compare what is new
new_no <- finn_Latest_scrape[!finn_Latest_scrape$url %in% no_Old$url,] 

# Add ID to our new data
ID <- nrow(no_Old)
IDcol <- c()
for (i in seq_len(nrow(new_no))) {
  ID <- ID + 1
  IDcol <- append(IDcol,20000+ID)
}
new_no <- cbind(IDcol,new_no)

# Choose what to put into clean sheet
new_for_clean_no <- new_no %>% select(IDcol,stillingstittel,arbetsgivare,sted,add_text,id)

# We want the date for the scrape to be in year-month-day
for (i in seq_len(nrow(new_for_clean_no))) {
  new_for_clean_no$id[i] <- substr(new_for_clean_no$id[i], start = 1, stop = 10)
}

# Change column names
colnames(new_for_clean_no) <- c("ID","Title", "Company","Location","Description","Scrape_date")

# Add to total of new data
new_for_clean_no[c("Hydrogen_relevance", "translatedText")] <- NA
new_data <- rbind(new_data,new_for_clean_no)
```

### Denmark

```{r}
#Compare what is new
new_dk <- dk_Latest_scrape[!dk_Latest_scrape$link_to_external_add %in% dk_Old$link_to_external_add,] 

# Add ID to our new data
ID <- nrow(dk_Old)
IDcol <- c()
for (i in seq_len(nrow(new_dk))) {
  ID <- ID + 1
  IDcol <- append(IDcol,30000+ID)
}
new_dk <- cbind(IDcol,new_dk)
```

We have an issue with the danish file. It is the "all_text" column which consists of cells containing more than 50k characters (which is the limit for google sheet). For this problem there are two solutions:

-   To shorten the texts by removing non-essential text

-   To compress the text into a shorter string. This string is then split into three different cells

For the sake of saving all information is both done.

```{r}
# Make a short_text column with "cleaned" text
remove_lines_with_pattern <- function(text, pattern) {
  # Pattern to match an entire line containing the specified pattern
  line_pattern <- paste0(".*", pattern, ".*\n?")
  str_replace_all(text, line_pattern, "")
}

pattern <-c("Cookiebot|DOMAINS|HTTP|www|/privacy|HTML|Thumbnails|Zoom|Cookie|cookie|ID|CONSENT|Samtykke|domains|consent|window|button|Expiry|SessionType:|/\|\\{|\\}")

ddk <- new_dk %>% 
  select(IDcol, all_text) %>%
  mutate(nr_breaks = str_count(all_text, pattern = "\n")) %>%
  mutate(nr_dots = str_count(all_text, pattern = "\\.")) %>%
  mutate(all_text_chr = str_length(all_text))

ddk_clean_breaks <- ddk %>%
  mutate(clean_breaks = map_chr(all_text, ~remove_lines_with_pattern(., pattern), .progress = T)) %>%
  mutate(clean_chr = str_length(clean_breaks))

df_short <- ddk_clean_breaks %>% select(IDcol, short_text = clean_breaks) %>% unique() 

dk_short <- new_dk %>% 
  left_join(df_short) %>%
  mutate(all_text_chr = str_length(all_text),
         short_text_chr = str_length(short_text)) 


new_dk$short_text <- dk_short$short_text

# Before the text is added we must check if any string still is too long - if so it cannot be uploaded 
for (i in seq_len(nrow(dk_short))) {
  if (dk_short$short_text_chr[i] > 50000) {
    new_dk$short_text[i] <- "UNSHORTABLE"
    new_for_clean_dk$short_text[i] <- paste("UNSHORTABLE -", new_dk$text[i], sep=" ")
  }
}

#-------------------------------------------------------------------------------------------#

# Define a function to compress a string
compress_string <- function(x) {
  compressed <- memCompress(charToRaw(x), type = "gzip")
  base64encode(compressed)
}

# Apply the function to the column in dataframe
new_dk$all_text <- lapply(new_dk$all_text, compress_string)

# Some tsrings are still too long in all_text, we will split them in three
split_string <- function(x) {
  n <- nchar(x)
  c1 <- substr(x, 1, min(50000, n))
  c2 <- ifelse(n > 50000, substr(x, 50001, min(100000, n)), "")
  c3 <- ifelse(n > 100000, substr(x, 100001, n), "")
  return(c(c1, c2, c3))
}

# Apply the function to dataframe
new_dk[c("all_text1", "all_text2", "all_text3")] <- t(apply(new_dk["all_text"], 1, split_string))

# Remove all_text
new_dk <- subset(new_dk, select = -all_text )
```

```{r}
# Choose what to put into clean sheet
new_for_clean_dk <- new_dk %>% select(IDcol,title,company,location,short_text,id)

# We want the date for the scrape to be in year-month-day
for (i in seq_len(nrow(new_for_clean_dk))) {
  new_for_clean_dk$id[i] <- substr(new_for_clean_dk$id[i], start = 1, stop = 10)
}

# Change column names
colnames(new_for_clean_dk) <- c("ID","Title", "Company","Location","Description","Scrape_date")

# Add to total of new data
new_for_clean_dk[c("Hydrogen_relevance", "translatedText")] <- NA
new_data <- rbind(new_data,new_for_clean_dk)
```

The function used to de-compress the compressed text is found in a separate section here.

```{r}
# How to de-compress

#decompress_string <- function(x) {
#  decompressed <- memDecompress(base64decode(x), type = "gzip")
#  rawToChar(decompressed)
#}

#dk_Latest_scrape$all_text <- lapply(dk_Latest_scrape$all_text, decompress_string)
```

## Clean & rename 

### Companies

Replaces the names of the companies in "new_data" with the new names from the worksheet, if there is no match it will be named "!!!NEW_COMPANY!!!".

```{r}
data_new_names <- new_data %>% 
  mutate(Company = case_when(tolower(str_trim(Company)) %in% tolower(comp_names$Old_name) ~ comp_names$New_name[match(tolower(str_trim(Company)),tolower(comp_names$Old_name))], TRUE ~ "!!!NEW_COMPANY!!!"))
```

### Locations

```{r}
for (i in seq_len(nrow(new_data))) {
  nr_matching <- 0
  for (j in seq_len(nrow(locations))) {
    if (grepl(locations$Name[j], new_data$Location[i], ignore.case = TRUE)) {
      #if true
      match <- locations$Name2[j] # save matching location name
      nr_matching <- nr_matching+1 # document how many matches we get
    } 
  }
  if (nr_matching == 0) {
    # if no matches were found must the locations list be updated to include more locations
    data_new_names$Location[i] <- "!!!NEW_LOCATION!!!"
  } else if (nr_matching > 1) {
    # if more than 1 match was found will the location choice have to be made manually
    data_new_names$Location[i] <- "!!!MULTIPLE_LOCATIONS!!!"
  } else {
    # when nr of matches is not 0 nor more than 1 will the found match be assigned to the add
    data_new_names$Location[i] <- match 
  }
}
```

# Upload changes to Google sheet

```{r}

```
