---
title: "Boxplots_barriers"
format: html
editor: visual
---

## Results from survey (Ranking barriers

Load results data

```{r}
library(dplyr)
library(googlesheets4)
library(tidyverse)
library(ggplot2)

# The following code will tell us how many observations per group that we need in order to get a statistically significant result. (k is number of gruops that we study)

pwr_result <- pwr.anova.test(k = 6, f = 0.25, sig.level = 0.05, power = 0.8) 
pwr_result


ss <- "https://docs.google.com/spreadsheets/d/1RefL2DMmCoOjCcIiaYgSnuDF34ORQFAZKu3nkaoS6o8/edit#gid=1219310046"

df <- read_sheet(ss, sheet = "ANOVA") #This is fake for now

```

Select and tidy the data

SKIP THIS STEP, GO WITH FAKE DATA FOR NOW !!

```{r}

# Select the ranking data

rank <- df %>% select(id,org_type,rank_barriers)
  
# Tidy the data
df1<- rank %>%
  separate_rows(rank_barriers,sep = ";")%>%  filter(rank_barriers != "") %>%
  mutate(rank_barriers = case_when(
             rank_barriers == "Experimentation and development by entrepreneurs - Developing business models and new pilot projects to lead the development further." ~ "Experiment",
             rank_barriers == "Guiding the direction of the search - Political and societal visions and goals of the technology." ~ "Guiding direction",
             rank_barriers == "Market formation - Creating a market for niche and early actors" ~ "Market formation",
             rank_barriers == "Knowledge development - Creation of new technology and knowledge within hydrogen." ~ "Knowledge development",
             rank_barriers == "Resource mobilisation - Access to competent work labour, material and capital." ~ "Resource mobilisation",
             rank_barriers == "Legitimization - Public and political acceptance and trust in the technology" ~ "Legitimization",
             rank_barriers == "Knowledge diffusion -Delning och kommunikation av kunskap mellan aktörer" ~ "Knowledge diffusion",
             TRUE ~ rank_barriers),counter=rep(7:1, length.out=n()))  # Counter in the end assigns a value to the barrier based on how high it was ranked
```

Plot a boxplot to be able to analyze the results, starting with the experimentation barrier for the 4 categories of respondents.

```{r}
exp <- df %>% filter(rank_barriers=="Experiment")


ggplot(exp, aes(x=org_type, y=counter)) +
  geom_boxplot(fill="skyblue", color = "black")+
  labs(title = "Experiment Barrier",
       x= "Group",
       y= "Value of barrier") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))


# To see if there is a statistically ignificant difference, run the code below and look at Pr(>F) if its below 0.05"*" is 95% sure that there is a significant difference to the respondants choise

#This means that some groups actually think that Experimentation is a more significant barrier than other groups. To know more about hte details, Post-hoc analysis/test is needed.

result <- aov(counter ~ org_type, data = exp)
summary(result)


```

Market formation barrier. Is there a difference between how they answer?

```{r}
mark <- df %>% filter(rank_barriers=="Market formation")


ggplot(mark, aes(x=org_type, y=counter)) +
  geom_boxplot(fill="skyblue", color = "black")+
  labs(title = "Experiment Barrier",
       x= "Group",
       y= "Value of barrier") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))

result <- aov(counter ~ org_type, data = mark)
summary(result)
```

Now we look at how each group have voted for the different barriers

```{r} # Just copy this code and change the org_type}
res <- df %>% filter(org_type=="Research")


ggplot(res, aes(x=rank_barriers, y=counter)) +
  geom_boxplot(fill="skyblue", color = "black")+
  labs(title = "Researchers view on different barriers",
       x= "Barrier",
       y= "Value of barrier") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))

result <- aov(counter ~ rank_barriers, data = res)
summary(result)
```

Extra code:

```{r}


ggplot(df1, aes(x=rank_barriers, y=counter)) +
  geom_boxplot(fill="skyblue", color = "black")+
  labs(title = "Ranking boxplot",
       x= "Category",
       y= "Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1))

ggplot(boxplot())

write_sheet(df1,ss, sheet = "ANOVA")

result <- aov(counter ~ rank_barriers, data = df1)
summary(result)

#Såå vad vi har här är en kod som bryter upp rankningen av barriärer
# till ett tidy data format, ger dom siffror efter vilken ordning de
#ligger i den kategoriserade ordningen. Detta blir som en värdering 
# av hur viktiga barriärerna är för varje svarande.

#frågan är nu då hur vi ska kategorisera för att hitta samband.
# Vi kan ju hitta om det är någonskillnad på hur de har röstat på en
# Specifik barriär. T:ex genom att plotta org.type på x axeln och 
# göra en plot per barriär

mean <- exp %>% group_by(org_type,rank_barriers)%>%
  summarise(mean_rank=mean(counter),.groups = "drop")%>%
  arrange(org_type,desc(mean_rank))
```
